Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-04-20 WholePlotTrajectories.Rmd
results

## Taxonomic and functional composition

@@

Except for leaf cholorphyll content, which displayed higher difference between plots than among treatments which may be due to the completeness of dataset, all CWM trajectories corresponded to significant changes after disturbance.
All functional traits and seed mass proportions displayed a unimodal trajectories but with different times at maximum and different values 30 years after disturbance. 
The weighted means of communities specific maximum height at adult stage (*Hmax*), leaf toughness (*L_toughness*) and wood specific gravity (*WD*) remained significantly lower than their initial value and than these of the control plots (Figure \@ref(fig:CWM)).
The weighted means of bark thickness (*Bark_thick*) similarly remained substantilly higher than initially for all disturbed plots while the specfic leaf area (*SLA*) had almost recovered its initial value and this of the undisturbed plots at the end of the experiment.

@@

## Disturbance impact on diversity

@@

For undisturbed plots the Richness, Shannon and Simpson diversity remained comparable to the initial values 5 years after disturbance.
After disturbance, the richness increased after low disturbance intensity, with a maximum increase of 14 botanical genuses (for plot 3 after treatment 2), but followed a unimodal decrease with a return to initial values after intense disturbance.
The taxonomic evenness (Shannon and Simpson diversities), however, significantly increased after all disturbance regime.
The evenness followed a unimodal trajectory with a just beginning return towards initial values and a maximum reached around 20 years and positively correlated to the disturbance intensity ($\rho_{spearman}^{Shannon}=0.86$, and $\rho_{spearman}^{Simpson}=0.89$).
Only two T3 plots, plots 8 and 12, remained increasing 30 years after disturbance \@ref(fig:DivTaxo)), suggesting a similar be much delayed unimodal trajectory.

@@

For all undisturbed plots the Rao diversity remained comparable to the initial values, 5 years after disturbance (1989 inventories).
The trajectories of all disturbed plots followed a unimodal trajectory with a maximum positively correlated to disturbance intensity ($\rho_{spearman}$) (Figure \@ref(fig:DivFun)). 
The plot 7 from treatment 1 was removed from the graphical representation for better readability, see appendix for full graph.
Thirty years after disturbance all plots, whenever the initial disturbance intensity, regained diversity values similar to their initial avule and to those of control plots.

@@

FunTraj(CompleteFun,remove=T)

>>>>

## Disturbance impacts on communities composition and average functional traits values

@@

Except for leaf cholorphyll content, which continued to increase for some T3 and T2 plots 30 years after disturbance, all traits and seed mass proportions displayed a unimodal trajectories.
The weighted means of communities specific maximum height at adult stage (*Hmax*), leaf toughness (*L_toughness*) and wood specific gravity (*WD*) remained significantly lower than their initial value and than these of the control plots (Figure \@ref(fig:CWM)).
The weighted means of bark thickness (*Bark_thick*) similarly remained substantilly higher than initially for all disturbed plots while the specfic leaf area (*SLA*) had almost recovered its initial value and this of the undisturbed plots at the end of the experiment.
Once again the maximum difference to initial state was correlated to the disturbance intensity ($\rho_{spearman}^{L_thickness}=0.67$,$\rho_{spearman}^{L_chloro}=0.45$,$\rho_{spearman}^{L_toughness}=-0.43$,$\rho_{spearman}^{SLA}=0.93$,$\rho_{spearman}^{WD}=-0.78$,$\rho_{spearman}^{Bark-thickness}=0.88$,$\rho_{spearman}^{Hmax}=-0.48$).

@@

## Trajectories of communities diversity after disturbance

@@

For undisturbed plots the Richness, Shannon and Simpson diversity remained stable over the 30 monitored years.
After disturbance the richness increased when the disturbance intensity was low, with a maximum increase of 14 botanical genuses (plot 3 from treatment 2).
When the disturbance was intense however, plot staxonomic richness followed a unimodal decrease with a return to initial values after intense disturbance.
The taxonomic evenness (Shannon and Simpson diversities) significantly increased whenever the disturbance intensity.
The evenness followed a unimodal trajectory with a just beginning return towards initial values and a maximum reached around 20 years and positively correlated to the disturbance intensity ($\rho_{spearman}^{Shannon}=0.86$, and $\rho_{spearman}^{Simpson}=0.89$).
Only two T3 plots, plots 8 and 12, remained increasing 30 years after disturbance \@ref(fig:DivTaxo)), suggesting a similar be much delayed unimodal trajectory.

@@

The functional diversity trajectories of plots based on the 8 leaf, stem and life history traits was examined through the Rao diversity.
For all undisturbed plots the functional diversity remained comparable to the reference values 5 years after disturbance (1989 inventories).
For all disturbed plots the functional trajectories followed a unimodal trajectory with a maximum positively correlated to disturbance intensity ($\rho_{spearman}=XX$) (Figure \@ref(fig:DivFun)). 
The plot 7 from treatment 1 that displayed a constantly outlying diversity was removed from the graphical representation for better readability, see appendix for full graph.
Thirty years after disturbance all plots, whenever the initial disturbance intensity, regained diversity values similar to their initial avule and to those of control plots.

@@

FunTraj(CompleteFun,remove=F)

### 2018-04-20 WholePlotTrajectories.tex
results

\subsection{Taxonomic and functional
composition}\label{taxonomic-and-functional-composition}

@@

Except for leaf cholorphyll content, which displayed higher difference
between plots than among treatments which may be due to the completeness
of dataset, all CWM trajectories corresponded to significant changes
after disturbance. All functional traits and seed mass proportions
displayed a unimodal trajectories but with different times at maximum
and different values 30 years after disturbance. The weighted means of
communities specific maximum height at adult stage (\emph{Hmax}), leaf
toughness (\emph{L\_toughness}) and wood specific gravity (\emph{WD})
remained significantly lower than their initial value and than these of
the control plots (Figure \ref{fig:CWM}). The weighted means of bark
thickness (\emph{Bark\_thick}) similarly remained substantilly higher
than initially for all disturbed plots while the specfic leaf area
(\emph{SLA}) had almost recovered its initial value and this of the
undisturbed plots at the end of the experiment.

@@

\subsection{Disturbance impact on
diversity}\label{disturbance-impact-on-diversity}

@@

For undisturbed plots the Richness, Shannon and Simpson diversity
remained comparable to the initial values 5 years after disturbance.
After disturbance, the richness increased after low disturbance
intensity, with a maximum increase of 14 botanical genuses (for plot 3
after treatment 2), but followed a unimodal decrease with a return to
initial values after intense disturbance. The taxonomic evenness
(Shannon and Simpson diversities), however, significantly increased
after all disturbance regime. The evenness followed a unimodal
trajectory with a just beginning return towards initial values and a
maximum reached around 20 years and positively correlated to the
disturbance intensity (\(\rho_{spearman}^{Shannon}=0.86\), and
\(\rho_{spearman}^{Simpson}=0.89\)). Only two T3 plots, plots 8 and 12,
remained increasing 30 years after disturbance \ref{fig:DivTaxo}),
suggesting a similar be much delayed unimodal trajectory.

@@

For all undisturbed plots the Rao diversity remained comparable to the
initial values, 5 years after disturbance (1989 inventories). The
trajectories of all disturbed plots followed a unimodal trajectory with
a maximum positively correlated to disturbance intensity
(\(\rho_{spearman}\)) (Figure \ref{fig:DivFun}). The plot 7 from
treatment 1 was removed from the graphical representation for better
readability, see appendix for full graph. Thirty years after disturbance
all plots, whenever the initial disturbance intensity, regained
diversity values similar to their initial avule and to those of control
plots.

>>>>

\subsection{Disturbance impacts on communities composition and average
functional traits
values}\label{disturbance-impacts-on-communities-composition-and-average-functional-traits-values}

@@

Except for leaf cholorphyll content, which continued to increase for
some T3 and T2 plots 30 years after disturbance, all traits and seed
mass proportions displayed a unimodal trajectories. The weighted means
of communities specific maximum height at adult stage (\emph{Hmax}),
leaf toughness (\emph{L\_toughness}) and wood specific gravity
(\emph{WD}) remained significantly lower than their initial value and
than these of the control plots (Figure \ref{fig:CWM}). The weighted
means of bark thickness (\emph{Bark\_thick}) similarly remained
substantilly higher than initially for all disturbed plots while the
specfic leaf area (\emph{SLA}) had almost recovered its initial value
and this of the undisturbed plots at the end of the experiment. Once
again the maximum difference to initial state was correlated to the
disturbance intensity
(\(\rho_{spearman}^{L_thickness}=0.67\),\(\rho_{spearman}^{L_chloro}=0.45\),\(\rho_{spearman}^{L_toughness}=-0.43\),\(\rho_{spearman}^{SLA}=0.93\),\(\rho_{spearman}^{WD}=-0.78\),\(\rho_{spearman}^{Bark-thickness}=0.88\),\(\rho_{spearman}^{Hmax}=-0.48\)).

@@

\subsection{Trajectories of communities diversity after
disturbance}\label{trajectories-of-communities-diversity-after-disturbance}

@@

For undisturbed plots the Richness, Shannon and Simpson diversity
remained stable over the 30 monitored years. After disturbance the
richness increased when the disturbance intensity was low, with a
maximum increase of 14 botanical genuses (plot 3 from treatment 2). When
the disturbance was intense however, plot staxonomic richness followed a
unimodal decrease with a return to initial values after intense
disturbance. The taxonomic evenness (Shannon and Simpson diversities)
significantly increased whenever the disturbance intensity. The evenness
followed a unimodal trajectory with a just beginning return towards
initial values and a maximum reached around 20 years and positively
correlated to the disturbance intensity
(\(\rho_{spearman}^{Shannon}=0.86\), and
\(\rho_{spearman}^{Simpson}=0.89\)). Only two T3 plots, plots 8 and 12,
remained increasing 30 years after disturbance \ref{fig:DivTaxo}),
suggesting a similar be much delayed unimodal trajectory.

@@

The functional diversity trajectories of plots based on the 8 leaf, stem
and life history traits was examined through the Rao diversity. For all
undisturbed plots the functional diversity remained comparable to the
reference values 5 years after disturbance (1989 inventories). For all
disturbed plots the functional trajectories followed a unimodal
trajectory with a maximum positively correlated to disturbance intensity
(\(\rho_{spearman}=XX\)) (Figure \ref{fig:DivFun}). The plot 7 from
treatment 1 that displayed a constantly outlying diversity was removed
from the graphical representation for better readability, see appendix
for full graph. Thirty years after disturbance all plots, whenever the
initial disturbance intensity, regained diversity values similar to
their initial avule and to those of control plots.
